### 2024-04-04 README.Rmd
Updated with bibliographic information

>>>>

## Paper

**A geo-referenced micro-data set of real estate listings for Spain’s three largest cities**

David Rey-Blanco and Pelayo Arbues (idealista)  
Fernando Lopez (Universidad Politecnica de Cartagena)  
Antonio Paez (McMaster University)

Published in *Environment and Planning B: Urban Analytics and City Science* (https://doi.org/10.1177/23998083241242844)
